\rule{\textwidth}{4pt}\\ \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payout Approximation in Discrete Space}\\[0.2cm] \rule{\textwidth}{2pt}

### 2025-02-12 latex/article.tex
cite
tikz

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\onehalfspacing
\DeclareMathOperator*{\argmin}{arg\,min}

% Define keywords command
\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\title{\rule{\textwidth}{4pt}\\
\textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm]
Regularized Payout Approximation in Derivative Space}\\[0.2cm]
\rule{\textwidth}{2pt}}
\author{\small \textbf{Vlad Kochetov} \\
    \small Faculty of Mechanics and Mathematics, \\
    \small Taras Shevchenko National University of Kyiv \\
    \small \texttt{vladkoch@knu.ua}
}
\date{\today}

@@

\keywords{
    \small{
        Vanilla Options, 
        Payout Profile, 
        Financial Engineering, 
        Option Pricing, 
        Approximation, 
        Numerical Methods,
        Quantitative Finance,
        Financial Derivatives,
        Computational Finance
    }
}

@@

\section{Literature Review}
Foundational work by Black and Scholes \cite{black1973pricing} established the theoretical framework for option pricing under geometric Brownian motion assumptions. Subsequent research has extended these principles to various derivative pricing applications.

\section{Methodology}
\subsection{Model Assumptions}
The analysis assumes the underlying asset follows geometric Brownian motion with constant drift $\mu$ and volatility $\sigma$ \cite{black1973pricing}:
\begin{equation}
dS_t = \mu S_t dt + \sigma S_t dW_t
\end{equation}
where $W_t$ is a Wiener process. Option pricing utilizes the Black-Scholes framework \cite{black1973pricing} for fair value calculation, incorporating risk-neutral valuation principles.

\subsection{Mathematical Framework}
Let \( V(S, T) \) represent the value of a target payout profile at maturity \( T \)
as a function of the underlying asset price \( S \). We construct an approximation
using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):

\begin{equation}
V(S, T) \approx \lambda S + \sum_{i=1}^{n} \alpha_i C(S, K_i, T) + \sum_{j=1}^{m} \beta_j P(S, K_j, T)
\end{equation}

where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) are
option weights. The optimal weights are found by solving the regularized least squares
problem:

\begin{equation}
\min_{\boldsymbol{\theta}} \int_{S_{\min}}^{S_{\max}} \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + \gamma \|\boldsymbol{\theta}\|_2^2
\end{equation}

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, and
\( S_{\min}, S_{\max} \) define the approximation domain.

@@

\begin{equation}
\boldsymbol{\theta}^* = \argmin_{\boldsymbol{\theta}} \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + \gamma \|\boldsymbol{\theta}\|_2^2
\end{equation}

@@

\subsection{Numerical Implementation}
The discrete optimization problem is solved using regularized least squares:
\begin{equation}
\boldsymbol{\theta}^* = (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} \mathbf{A}^\top \mathbf{b}
\end{equation}

where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix for L2 regularization. Evaluation points $\{S_k\}$ are typically distributed around the current spot price to emphasize approximation accuracy in relevant price regions.

\section{Results}
\subsection{Distribution-Based Trading Strategy}
The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions. Traders can hedge against forecasted distribution features, express views on higher moments of price distribution, and implement volatility surface arbitrage strategies through carefully constructed option portfolios.

@@

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of L1 and L2 regularization methods for payout profile approximation}
\label{fig:regularization}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\onehalfspacing
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{amsmath, amssymb, amsthm}

% Define keywords command
\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\title{\rule{\textwidth}{4pt}\\
\textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm]
Regularized Payout Approximation in Discrete Space}\\[0.2cm]
\rule{\textwidth}{2pt}}
\author{\small \textbf{Vlad Kochetov} \\
    \small Faculty of Mechanics and Mathematics, \\
    \small Taras Shevchenko National University of Kyiv \\
    \small \texttt{vladkoch@knu.ua}
}
\date{\today}

@@

\keywords{
    \small{
        Vanilla Options, 
        Payout Profile, 
        Financial Engineering, 
        Option Pricing, 
        Approximation, 
        Numerical Methods,
        Quantitative Finance,
        Financial Derivatives,
        Computational Finance,
        Distribution Forecasts,
        Portfolio Construction,
        Option Trading
    }
}

@@

\section{Literature Review}

\section{Methodology}
\subsection{Model Assumptions}

\subsection{Mathematical Framework}
Let \( V(S) \) represent the value of a target payout profile as a function of the underlying asset price \( S \). We construct an approximation using \( n \) call options and \( m \) put options with strike prices \( \{K_i\}_{i=1}^{n+m} \):

\begin{equation}
V(S) \approx \lambda S + \sum_{i=1}^{n} \alpha_i C(S, K_i) + \sum_{j=1}^{m} \beta_j P(S, K_j)
\end{equation}

where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) are
option weights. The optimal weights are found by solving the regularized least squares
problem with either L2 (Ridge) or L1 (Lasso) regularization:

\begin{equation}
\min_{\boldsymbol{\theta}} \int_{S_{\min}}^{S_{\max}} \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + \gamma \|\boldsymbol{\theta}\|_p^p
\end{equation}

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, 
\( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight distributions,
while the L1 norm (\(p=1\)) tends to produce sparse solutions by setting some weights
exactly to zero, which can be beneficial when portfolio simplicity or transaction costs
are important considerations.

@@

\begin{equation}
\boldsymbol{\theta}^* = \argmin_{\boldsymbol{\theta}} \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + \gamma \|\boldsymbol{\theta}\|_p^p
\end{equation}

@@

\subsection{Numerical Implementation}
The discrete optimization problem with L2 regularization has a closed-form solution:
\begin{equation}
\boldsymbol{\theta}^* = (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} \mathbf{A}^\top \mathbf{b}
\end{equation}

where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ controls solution smoothness through regularization, and $\mathbf{I}$ denotes the identity matrix. Evaluation points $\{S_k\}$ are typically distributed around the current spot price to emphasize approximation accuracy in relevant price regions. The L1-regularized problem is solved using iterative optimization methods.

\section{Results}
\subsection{Distribution-Based Trading}
The approximation method enables novel trading strategies that exploit distributional forecasts rather than direct price predictions. Traders can hedge against forecasted distribution features, express views on higher moments of price distribution, and implement volatility surface arbitrage strategies through carefully constructed option portfolios.

@@

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of regularization methods using 9 strike prices.}
\label{fig:regularization}
\end{figure}
